Example script the `dispRity` paper

### 2018-03-22 inst/gitbook/02_getting-started.Rmd
Minor changes to push for vignette

### Ordination matrices from `Claddis`

@@

>>>>

@@

### Ordination matrices from `Claddis` {#Claddis-ordination}

> This functionality is not available on the CRAN version of the package (1.0.3)<!-- versiontagCRAN --> due to CRAN compatibility issues see [to CRAN or not to CRAN?](#noCRAN) for more information and on how to install the GitHub (more complete) version of the package (1.1)<!-- versiontagGH -->.

### 2018-03-22 inst/gitbook/index.Rmd
Minor changes to push for vignette

You can install this package easily if you use the latest version of `R` (> 3.4.0) and `devtools`.

@@

## Installing the latest released version directly from GitHub
install_github("TGuillerme/dispRity", ref = "release")

## Loading the package
library(dispRity)
```

@@

Note this uses the `release` branch (version`0.5`). <!-- @@@ -->
For the piping-hot (but potentially unstable) version, you can change the argument `ref = release` to `ref = master`.
`dispRity` depends mainly on the `ape` package and uses functions from several other packages (`ade4`, `geometry`, `grDevices`, `hypervolume`, `paleotree`, `snow`, `Claddis`, `geomorph` and `RCurl`).

## Why not CRAN?

This package is not available on CRAN.
This is mainly because some parts are still in development and that the reactivity of GitHub is better for implementing new suggestions from users.
However, the package follows the strict (and useful!) CRAN standards via Travis.

<!-- badges out start -->
[![Build Status](https://travis-ci.org/TGuillerme/dispRity.svg?branch=release)](https://travis-ci.org/TGuillerme/dispRity)
[![codecov](https://codecov.io/gh/TGuillerme/dispRity/branch/master/graph/badge.svg)](https://codecov.io/gh/TGuillerme/dispRity)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges out end   -->

>>>>

You can install this package easily, directly from the CRAN:

```{r, eval = FALSE}
install.packages("dispRity")
```

Alternatively, for the most up to data version and some functionalities not compatible with the CRAN, you can use the package through GitHub using `devtool` (see [to CRAN or not to CRAN?](#noCRAN) for more details):

@@

## Installing the latest released version directly from GitHub
install_github("TGuillerme/dispRity", ref = "release")
```

Anyways to upload it, you can use

@@

Note this uses the `release` branch (1.1)<!-- versiontagGH -->.
For the piping-hot (but potentially unstable) version, you can change the argument `ref = release` to `ref = master`.
`dispRity` depends mainly on the `ape` package and uses functions from several other packages (`ade4`, `geometry`, `grDevices`, `hypervolume`, `paleotree`, `snow`, `Claddis`, `geomorph` and `RCurl`).

## To CRAN or not to CRAN? {#noCRAN}

This package can be installed via [the CRAN]() or via [GitHub](https://github.com/TGuillerme/dispRity).

 * The CRAN version is a more "strict" version of the package that does not include some functionalities (such as [`Claddis.ordination`](#Claddis-ordination) or this gitbook vignette) because of compatibility issues with the CRAN requirement.

 * The GitHub version is a more "reactive" version (fed by user's suggestions and comments) and can contain more functionalities (see list below). This version exists on a `"release"` branch which is tested as strictly as the CRAN version with Travis and codecov. The `"master"` branch contains always the latest "piping hot", not yet release version. It might (though rarely) be bugged.

<!-- badges out start -->
[![Build Status](https://travis-ci.org/TGuillerme/dispRity.svg?branch=release)](https://travis-ci.org/TGuillerme/dispRity)
[![codecov](https://codecov.io/gh/TGuillerme/dispRity/branch/release/graph/badge.svg)](https://codecov.io/gh/TGuillerme/dispRity)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges out end   -->

Note however, that apart from the functions listed below, both versions of the package have the same tested and implemented functions.

Functions not available on the CRAN version (1.0.3)<!-- versiontagCRAN -->:

 * [`Claddis.ordination`](#Claddis-ordination)

### 2018-03-22 paper/dispRity_paper.tex
Minor changes to push for vignette

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{dispRity_fun.pdf} 
\caption{Illustration of the different metric dimension-levels in the \disp package. In this example, each cell corresponds to a single value (e.g. a 8 $\times$ 7 matrix or a vector of eight elements).
A dimension-level 3 matrix would be a metric output a matrix (e.g. the function \texttt{stats::cor} to calculate the correlation between each dimension), a dimension-level 2 metric would output a vector (i.e. a distribution, e.g. \texttt{dispRity::variances} which calculates the variance within each dimension) and a dimension-level 1 metric would output a single value (e.g. \texttt{stats::sd} which calculates the standard deviation of the input matrix)}.
\label{Fig:levels}
\end{figure}

@@

\section{Package location}
The \disp package is available at \url{https://github.com/TGuillerme/dispRity}.
The latest released versions can be directly loaded in \texttt{R} using the following command:

\noindent \texttt{> if(!require(devtools)) install.packages("devtools")}\\
\noindent \texttt{> install\_github("TGuillerme/dispRity", ref = "release")}

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{dispRity_fun.pdf}  %../inst/gitbook/dispRity_fun.pdf} 
\caption{Illustration of the different metric dimension-levels in the \disp package. In this example, each cell corresponds to a single value (e.g. a 8 $\times$ 7 matrix or a vector of eight elements).
A dimension-level 3 matrix would be a metric output a matrix (e.g. the function \texttt{stats::cor} to calculate the correlation between each dimension), a dimension-level 2 metric would output a vector (i.e. a distribution, e.g. \texttt{dispRity::variances} which calculates the variance within each dimension) and a dimension-level 1 metric would output a single value (e.g. \texttt{stats::sd} which calculates the standard deviation of the input matrix)}.
\label{Fig:levels}
\end{figure}

@@

\section{Package location}
The \disp package is available on the CRAN or at \url{https://github.com/TGuillerme/dispRity} with more associated information.
